A scenario for a Planckian standard kilogram

### 2017-11-30 manuscript_gravitationalconstant.tex
some edits

\begin{abstract}
The kilogram could, in principle, be redefined as an integer multiple
of the Planck mass (or 4594xxxx$\times\sqrt{\hbar c/G}$) with no
significant change from its current value.  The practical hurdle is
measuring $G$ three or four orders of magnitude better than currently
known, so as to find the unknown digits xxxx.  We study a possible
scenario for doing so with an artificial two-body orbit.  The cleanest
(admittedly, not the cheapest) option is to place the system on a
Trojan orbit to minimize external gravitational perturbations, and
enclose it in a cavity chilled to liquid-helium temperatures, to
suppress radiation pressure.  Data analysis would involve
marginalizing over at least 15~nuisance parameters (6~for orbital
parameters and 9~for fictitious forces) but that, we show, is
feasible.
\end{abstract}

@@

\section{A new approach to measure $G$}
In Fig.~\ref{fig:Gmeasurements} we plot the best-known recent
measurements of the gravitational constant. Three of them
(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14} and
HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
UZur-06\cite{Schlamminger06} used a beam balance, and
JILA-10\cite{Parks10} measured the separation of two simple pendulums
in a gravitational field. They all tried to measure the very weak
gravitational force with a mechanical apparatus. The sixth measurement
(LENS-14\cite{Rosi14}) was performed with another approach, using cold
atom interferometry. Its uncertainty is a lot larger than the others,
but it could become more competitive in the future. However, a brief
glance on the plotted measurements shows the disagreement of current
$G$-values and suggests a demand for new, potentially different
techniques.

@@

>>>>

\begin{abstract}
As the kilogram assumes its new definition in terms of $h,c,$ and the
standard second, it is interesting to think about a possible future
definition entirely in terms of fundamental constants.  A kilogram
defined as an integer multiple of the Planck mass (or
4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
from its current value.  The practical hurdle to this Planckian
kilogram is measuring $G$ three or four orders of magnitude better
than currently known, so as to find the unknown digits xxxx.  We study
a possible scenario for doing so with an artificial two-body orbit.
The cleanest (admittedly, not the cheapest) option is to place the
system on a Trojan orbit to minimize external gravitational
perturbations, and enclose it in a cavity chilled to liquid-helium
temperatures, to suppress radiation pressure.  Data analysis would
involve marginalizing over at least 15~nuisance parameters (6~for
orbital parameters and 9~for fictitious forces) but that, we show, is
feasible.
\end{abstract}

@@

\section{A new approach to measure $G$}
In Fig.~\ref{fig:Gmeasurements} we plot the best-known recent
measurements of the gravitational constant. Three of them
(BIPM-14,\cite{Quinn14} UCI-14,\cite{Newman14} and
HUST-09\cite{Luo09}) were carried out using a torsion balance, whereas
UZur-06\cite{Schlamminger06} used a beam balance, and
JILA-10\cite{Parks10} measured the separation of two simple pendulums
in a gravitational field. They all tried to measure the very weak
gravitational force with a mechanical apparatus. The sixth measurement
(LENS-14\cite{Rosi14}) was performed with another approach, using cold
atom interferometry. Its uncertainty is a lot larger than the others,
but it could become more competitive in the future. However, a brief
glance on the plotted measurements shows the disagreement of current
$G$-values and suggests a demand for new, potentially different
techniques.  One remarkable idea is to use the helioseismic modes of
the Sun, because they depend on both the mass and $G$ times the mass
of the Sun,\cite{Ch-Dalsgaard05} but this strategy does not yet give
competitive accuracy in $G$.

@@

\bibitem{Ch-Dalsgaard05} J. Christensen-Dalsgaard, M.~P. Di Mauro,
  H. Schlattl and A. Weiss, ``On helioseismic tests of basic
  physics'', \textit{MNRAS}, 356:587--595 (2005).
